Draft1

### 2014-12-12 PresentationandPaper/Draft1.Rmd
Added Latex to set single spacing in tables

# Generate descriptive statistics table
stargazer(CD1, type = "latex")
```

@@

Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the dependent variables we selected as indicators of the entrepreneurship rate.  Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant when using "Nascent Entrepreur" or "Business Owner" as a dependent variable, has a negative coefficient in these regression equations.  This relationship can be seen in the following regression output table.  This regression output was generated using a simple least square regression model.

@@

```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}

@@

To more clearly demonstrate the relationship between the "Way of Teaching" and our dependent variables, we have omitted the country-specific effects and generated simulations to show demonstrate the outcome of 1000 trials of our regression equation.  Before doing so, however, we ran another set of regressions to determine which equation we would like to examine more closely.  A regression output table with these results has been included below.

@@

<br>
```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}

@@

@@

# Regression output table with country-specific effects
stargazer::stargazer(Z1, Z2,
                     title = 'Least Squares Regression for Continuous Dependent Variables',
                     covariate.labels = labels_1, dep.var.labels = dlabels_2, digits = 2,
                     font.size =  "scriptsize", type = 'latex', no.space = TRUE,
                     notes = "Regression equation 1 is unimputed, regression equation 2 is imputed")
```

>>>>

\begin{singlespace}
```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis', warning=FALSE}

# Generate descriptive statistics table
stargazer(CD1, type = "latex")
```
\end{singlespace}

@@

Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the dependent variables we selected as indicators of the entrepreneurship rate.  Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant when using "Nascent Entrepreur" or "Business Owner" as a dependent variable, has a negative coefficient in these regression equations.  This relationship can be seen in table 4 below.  This regression output was generated using a simple least square regression model.

@@

\begin{singlespace}
```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}

@@

```
\end{singlespace}

To more clearly demonstrate the relationship between the "Way of Teaching" and our dependent variables, we have omitted the country-specific effects and generated simulations to show demonstrate the outcome of 1000 trials of our regression equation.  Before doing so, however, we ran another set of regressions to determine which equation we would like to examine more closely.  The results can be seen in table 5 below.

@@

\begin{singlespace}
```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}

@@

```
\end{singlespace}

@@

# Regression output table with country-specific effects
stargazer::stargazer(Z1, Z2,
                     title = 'Least Squares Regression for Continuous Dependent Variables',
                     covariate.labels = labels_1, dep.var.labels = dlabels_2, digits = 2,
                     font.size =  "small", type = 'latex', no.space = TRUE,
                     notes = "Regression equation 1 is unimputed, regression equation 2 is imputed")
```
\end{singlespace}
